---
title: "2021_week3_Tate_artwork"
author: "Emma Skarstein"
date: "September 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Loading data and libraries

```{r}
library(tidyverse)
```

```{r}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

tuesdata <- tidytuesdayR::tt_load(2021, week = 3)
artwork <- tuesdata$artwork
artists <- tuesdata$artists
```

# Data Dictionary

## `artwork.csv`

|variable           |class     |description |
|:------------------|:---------|:-----------|
|id                 |double    | Unique ID |
|accession_number   |character | Accession number |
|artist             |character | Artist Name |
|artistRole         |character | Artist or other attribution |
|artistId           |double    | Artist ID |
|title              |character | Title of the piece of art |
|dateText           |character | Date as raw text (pretty messy) |
|medium             |character | Medium of art, quite a lot of overlap |
|creditLine         |character | How acquired |
|year               |double    | Year of creation |
|acquisitionYear    |double    | Year acquired |
|dimensions         |character | Dimensions as character |
|width              |double    | Width of art |
|height             |double    | Height of art |
|depth              |double    | Depth of art |
|units              |character | units of measure |
|inscription        |character | inscription if present |
|thumbnailCopyright |logical   | Thumbnail copyright|
|thumbnailUrl       |character | Thumbnail URL |
|url                |character | art URL |

## `artists.csv`

|variable     |class     |description |
|:------------|:---------|:-----------|
|id           |double    | Artist ID |
|name         |character | Artist Name |
|gender       |character | Artist gender|
|dates        |character | Date as a character |
|yearOfBirth  |double    | Year of birth |
|yearOfDeath  |double    | Year of death |
|placeOfBirth |character | Place of birth (typically city, country) |
|placeOfDeath |character | Place of death (typically city, country) |
|url          |character | Artist URL |

# Doing stuff

```{r}
art_artist <- right_join(artists, artwork, by = c("name" = "artist"))

ggplot(art_artist, aes(x = year, fill = gender)) +
  geom_bar()

ggplot(art_artist, aes(x = acquisitionYear, fill = gender)) +
  geom_bar()

female_art <- art_artist %>% dplyr::filter(gender == "Female")
min(female_art$year, na.rm = TRUE)
min(female_art$acquisitionYear, na.rm = TRUE)

```

```{r}
library(ggplot2)
p <- ggplot(mtcars, aes(x=wt, y=mpg)) + geom_point() +
  ggtitle("Fuel Efficiency of 32 Cars") +
  xlab("Weight (x1000 lb)") + ylab("Miles per Gallon") +
  theme(text=element_text(size=16, family="Impact"))
p

library(showtext)
font_add_google(name = "Roboto Condensed") 
# turn on showtext
showtext_auto()

font_add(family = "docktrin", regular = "./Fonts/docktrin/docktrin.ttf")
showtext_auto()



library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Gochi Hand", "gochi")
font_add_google("Schoolbell", "bell")


font_add_google("Proxima Nova")

## Automatically use showtext to render text
showtext_auto()

set.seed(123)
hist(rnorm(1000), breaks = 30, col = "steelblue", border = "white",
     main = "", xlab = "", ylab = "")
title("Histogram of Normal Random Numbers", family = "bell", cex.main = 2)
title(ylab = "Frequency", family = "Roboto Condensed", cex.lab = 2)
text(2, 70, "N = 1000", family = "Lora", cex = 2.5)
```




